---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Ye Tian"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = Deaths, fill = race)) + 
    geom_bar(position = "fill")
```
If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
ggplot(covid_data_long, aes(x = race, fill = race)) + 
    geom_bar()
```
1. Write code for a plot and describe what you observe?
I used the covid-data-long data set to plot a bar chart describing the number of cases among different races in the US.
2. Are there any conclusions you can draw?
Among all the race and ethnicity, most number of cases are white population, and the least number of cases are the multiracial population.
3. What were you not able to do due to not having the R knowledge?
I wanted to find out the proportion of individuals who got Covid to the total population among different states. However, I was not able to recall the correct function, and there seem to be too many states to show in a single plot. I am not sure if it is viable to do that.
4. What other data would be useful to better understand this data?
Since I was intended to show the proportion of deadth cases to each covid cases, it is ideal to showcase the number of death cases to understand the data.

